Texture mapping 3D planar models of indoor environments with noisy camera poses

### 2012-12-31 spie/_region_.tex
nead final result and wrapup now

\documentclass[]{spie}  %>>> use for US letter paper
%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
%% \addtolength{\voffset}{9mm}   %>>> moves text field down
%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
%  The following command loads a graphics package to include images 
%  in the document. It may be necessary to specify a DVI driver option,
%  e.g., [dvips], but that may be inappropriate for some LaTeX 
%  installations. 
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{caption}
\usepackage{subcaption}

@@

\message{ !name(paper.tex) !offset(674) }
\subsection{Future stuff}
For the sake of simplicity, - cases where multiple whatever are few,
but for true generality, should go to 3d adjustments

\begin{figure*}
  \centering
  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
  ~~~~~~~~
  \centering
  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}

  \centering 
  \subfloat[][]{\includegraphics[height=2in, width=3in]{floorcropped.jpg}}
  ~~~~~~~~
  \centering
  \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
  \caption{Examples of our final texture mapping output for (a) walls,
    (b) ceilings, (c) an entire floor, (d) a full model.}
  \label{fig:results}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% References %%%%%

\bibliography{report} %>>>> bibliography data in report.bib
\bibliographystyle{spiebib} %>>>> makes bibtex use spiebib.bst

\message{ !name(paper.tex) !offset(672) }

>>>>

\documentclass[]{spie}  %>>> use for US letter paper
%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
%% \addtolength{\voffset}{9mm}   %>>> moves text field down
%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
%  The following command loads a graphics package to include images 
%  in the document. It may be necessary to specify a DVI driver option,
%  e.g., [dvips], but that may be inappropriate for some LaTeX 
%  installations. 
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

@@

\message{ !name(paper.tex) !offset(278) }
\subsection{Geometry-based Alignment}
\label{sec:geometryAlignment}
After computing each image's projection onto the target surface, as
described in Section \ref{sec:simpleTextureMapping}, we detect lines
in the projections using Hough transforms. Experience and intuition
show that walls in indoor environments contain linear features that
are either horizontal or vertical, often corresponding to doors,
windows, posters, etc. Thus, when texturing walls, we rotate images in
2D such that dominant lines are made to be horizontal or
vertical. This can be further extrapolated by orienting lines with a
wall's boundaries, for example in areas with a slanted roof.

\begin{figure}
  \centering
  \includegraphics[height=1.5in]{geometryAlign_planes.png}
  \includegraphics[height=1.5in]{geometryAlignment.jpg}
  \caption{(a) When texturing the red surface, it makes sense to align images to surface boundaries and intersections. (b) Red lines are geometry-based lines, while green lines are detected in the image via Hough transform. Above is the original projection, and below is the image adjusted for alignment.}
  \label{fig:geometryAlignment}
\end{figure}

At this point in time, image occlusions have not been accounted
for. As a result, some image projections contain texture that should
project to an adjacent surface, generally with a linear boundary where
the two surfaces meet. If this linear boundary is detected by Hough
transform, the image is rotated and shifted in 2D such that the visual
boundary between two surfaces matches the physical boundary in our
digital model. An example of such an adjustment is in Figure
\ref{fig:geometryAlignment}

To perform the rotation and alignment, one method would be to detect
all line matches and solve for an optimal homography. In nearly all
cases however, we find that a single 2D rotation is sufficient to
properly align lines in an image. We also rarely have more than one
linear geometry feature to match to in each orthogonal
direction. Thus, for a rotation angle, we simply take all angles
between image-based and geometry-based lines under 5 degrees, and
average them. After the image is rotated, we find the horizontal and
vertical image-based and geometry-based line segments with minimum
orthogonal distance between them. For both distances, if it is under 5
mm, we apply the corresponding shift, and indicate that the image was
aligned to geometry in one or both dimensions, which reduces further
shifting in Section \ref{sec:robustSIFTFeatureMatching}.

\message{ !name(paper.tex) !offset(679) }

### 2012-12-31 spie/paper.tex
nead final result and wrapup now

The remainder of the paper is organized as follows. Section
\ref{sec:simpleTextureMapping} explains how input images are projected
onto our geometry and simple approaches towards texturing. Section
\ref{sec:existingApproaches} covers more sophisticated existing
approaches to image matching and stitching, and their performance on
our datasets. Section \ref{sec:imageAlignment} contains our approach
towards image alignment, followed by Section
\ref{sec:imageCompositing}, which describes compositing
approaches. Section \ref{sec:resultsAndConclusions} contains further
results and conclusions, as well as areas of ongoing and future work.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
  \centering
  \includegraphics[height=1.5in]{geometryFeature.jpg}
  \includegraphics[height=1.5in]{imageCorner.jpg}
  \includegraphics[height=1.5in]{geometryImageAlign.jpg}
  \caption{(a) The red lines indidcate geometry-based lines,
    consisting of boundaries and intersections. (b) A matching
    image-based line, corresponding to a corner. (c) The image rotated
    and shifted such that the matched lines align align with
    geometry.}
  \label{fig:geometryAlignment}
\end{figure}

@@

The $N \times M$ matrix $A$ is constructed with one row for each pair
of images with measured distances produced by the SIFT matching
stage. A row in the matrix has a $-1$ and $1$ in the columns
corresponding to the two images in the pair. For example, the matrix
below indicates a SIFT-based distance between images 1 and 2, images 1
and 3, images 2 and 3, etc.
\[
A =
\begin{pmatrix}
  -1 & 1 & 0 & \cdots & 0 & 0\\
  -1 & 0 & 1 & \cdots & 0 & 0\\
  0 & -1 & 1 & \cdots & 0 & 0\\
  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
  0 & 0 & 0 & \cdots & 1 & 0 \\
  0 & 0 & 0 & \cdots & -1 & 1 \\
  1 & 0 & 0 & \cdots & 0 & 0\\
\end{pmatrix}
\]
If only relative distances between images are included, the absolute
location of the images can not be calculated, and the matrix is rank
deficient. From Section \ref{geometryBasedAlignemtn}, a number of
images are anchored to geometry points, in one or both dimensions, and
thus their locations can be used to fix the rest in place. In case no
anchor images exist, we simply arbitrarily pick an image, as we have
no other reference points to work with. In the above matrix, the first
image is set to be such an anchor, simply by placing a $1$ in its
column.

>>>>

The remainder of the paper is organized as follows. Section
\ref{sec:simpleTextureMapping} explains how input images are projected
onto our geometry and simple approaches towards texturing. Section
\ref{sec:existingApproaches} covers more sophisticated existing
approaches to image matching and stitching, and their performance on
our datasets. Section \ref{sec:2dAlignment} contains our approach
towards image alignment, followed by Section
\ref{sec:imageCompositing}, which describes compositing
approaches. Section \ref{sec:resultsAndConclusions} contains further
results and conclusions, as well as areas of ongoing and future work.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
  \centering
  \includegraphics[height=1.5in]{geometryAlign_planes.png}
  \includegraphics[height=1.5in]{geometryAlignment.jpg}
  \caption{(a) When texturing the red surface, it makes sense to align images to surface boundaries and intersections. (b) Red lines are geometry-based lines, while green lines are detected in the image via Hough transform. Above is the original projection, and below is the image adjusted for alignment.}
  \label{fig:geometryAlignment}
\end{figure}

@@

The $N \times M$ matrix $A$ is constructed with one row for each pair
of images with measured distances produced by the SIFT matching
stage. A row in the matrix has a $-1$ and $1$ in the columns
corresponding to the two images in the pair. For example, the matrix
below indicates a SIFT-based distance between images 1 and 2, images 1
and 3, images 2 and 3, etc.
\[
A =
\begin{pmatrix}
  -1 & 1 & 0 & \cdots & 0 & 0\\
  -1 & 0 & 1 & \cdots & 0 & 0\\
  0 & -1 & 1 & \cdots & 0 & 0\\
  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
  0 & 0 & 0 & \cdots & 1 & 0 \\
  0 & 0 & 0 & \cdots & -1 & 1 \\
  1 & 0 & 0 & \cdots & 0 & 0\\
\end{pmatrix}
\]
If only relative distances between images are included, the absolute
location of the images can not be calculated, and the matrix is rank
deficient. From Section \ref{sec:geometryAlignment}, a number of
images are anchored to geometry points, in one or both dimensions, and
thus their locations can be used to fix the rest in place. In case no
anchor images exist, we simply arbitrarily pick an image, as we have
no other reference points to work with. In the above matrix, the first
image is set to be such an anchor, simply by placing a $1$ in its
column.
